Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 nge.tex

The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for communication
and coordination of the execution of units. ORTE is a critical component of the
OpenMPI implementation, developed to support distributed high-performance
computing applications operating in a heterogeneous environment~\cite{castain05:_open_rte, cug-2016}.  
 ORTE transparently provides support for interprocess communication, resource discovery and allocation, and process launching across a variety of platforms. ORTE provides a mechanism similar to the Pilot concept -
it allows the user to create a \emph{``dynamic virtual machine''} (DVM) that
spans multiple nodes. ORTE provides libraries to enable the submission,
monitoring and managing of tasks, avoiding filesystem bottlenecks and race
conditions with network sockets. As a consequence, it is able to minimize the
system overhead while submitting tasks.

>>>>

The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for communication
and coordination of the execution of units. ORTE is a critical component of the
OpenMPI implementation, developed to support distributed high-performance
computing applications operating in a heterogeneous environment~\cite{castain05:_open_rte, cug-2016}.  
 ORTE transparently provides support for interprocess communication, resource discovery and allocation, and process launching across a variety of platforms. ORTE provides a mechanism similar to the Pilot concept -
it allows the user to create a \emph{``dynamic virtual machine''} (DVM) that
spans multiple nodes. ORTE provides libraries to enable the submission,
monitoring and managing of tasks, avoiding filesystem bottlenecks and race
conditions with network sockets. 
\aanote{Requires validation: Alternative version of the three sentences above (too many ORTE in my opinion): 
ORTE provides a mechanism similar to the Pilot concept - it allows the user to create a \emph{``dynamic virtual machine''} (DVM) that spans multiple nodes. The DVM transparently provides support for interprocess communication, resource discovery and allocation, and process launching across a variety of platforms. 
Libraries allow the interaction between users and ORTE to enable the submission,
monitoring and managing of tasks, avoiding filesystem bottlenecks and race
conditions with network sockets. 
}

As a consequence, ORTE is able to minimize the
system overhead while submitting tasks.
